---
title: "Getting Started with flixpatrol"
---

This article demonstrates how to use the flixpatrol package to retrieve streaming platform rankings and analytics from the FlixPatrol API.

## Setup

First, load the package and set your API key:

```{r}
#| label: setup-library
#| eval: false
library(flixpatrol)

# Set your API key (do this once in your .Renviron)
usethis::edit_r_environ()
# Add: FLIX_PATROL=your_api_key_here
```

To suppress lookup messages globally:

```{r}
#| label: setup-options
#| eval: false
options(flixpatrol.silent = TRUE)
```

## Looking Up IDs

Before fetching data, you often need to translate human-readable names to FlixPatrol IDs.

### Countries and Platforms

```{r}
#| label: lookup-country-platform
#| eval: false
# Single lookup
lookup_country("United States")
#> [1] "cnt_iMUHNbZvnNHK5YdhgwtOoP4u"

lookup_platform("Netflix")
#> [1] "cmp_IA6TdMqwf6kuyQvxo9bJ4nKX"

# Multiple at once (vectorized)
lookup_country(c("United States", "Germany", "Japan"))
#> [1] "cnt_iMUHNbZvnNHK5YdhgwtOoP4u" "cnt_7KpRmXvZqL2nYwT9hJcF3sMd"
#> [3] "cnt_8NqSmYwArM3oZxU0iKdG4tNe"

lookup_platform(c("Netflix", "Disney+", "HBO Max"))
#> [1] "cmp_IA6TdMqwf6kuyQvxo9bJ4nKX" "cmp_2BqTnOwZs7lPaRv1jLdH5uPf"
#> [3] "cmp_3CrUoPxAt8mQbSw2kMeI6vQg"
```

### Titles and Franchises

```{r}
#| label: lookup-title-franchise
#| eval: false
lookup_title("Squid Game")
#> [1] "ttl_yPCJU2UzROTNVv5JZ7Hu4m8M"

lookup_franchise("Marvel")
#> [1] "frn_KGBes9dtvkV710raDBpXoKRc"
```

### Reverse Lookup (ID to Name)

```{r}
#| label: reverse-lookup
#| eval: false
# Works with any ID type (cmp_, ttl_, frn_)
get_title_name("cmp_IA6TdMqwf6kuyQvxo9bJ4nKX")
#> [1] "Netflix"

# Vectorized - returns NA for failures
get_title_name(c("cmp_IA6TdMqwf6kuyQvxo9bJ4nKX", "ttl_invalid"))
#> [1] "Netflix" NA
```

## Fetching Top 10 Rankings

### Daily Top 10

```{r}
#| label: get-top-ten
#| eval: false
# Get a week of Top 10 data
top10 <- get_top_ten(
  platform_name = "netflix",
  country_name  = "United States",
  start_date    = "2025-12-01",
  end_date      = "2025-12-07",
  media_type    = "movie"
)

top10
#> # A tibble: 70 x 7
#>     rank title                  type_id days_total rank_last date       imdb_id
#>    <int> <chr>                    <int>      <int>     <int> <chr>        <int>
#>  1     1 Carry-On                     1         15         1 2025-12-01  123456
#>  2     2 The Six Triple Eight         1          8         2 2025-12-01  234567
#>  3     3 Our Little Secret            1         21         3 2025-12-01  345678
#> # i 67 more rows
```

### Filtering Results

```{r}
#| label: filter-top-ten
#| eval: false
library(dplyr)

# Find #1 movies each day
top10 |>
  filter(rank == 1) |>
  select(date, title, days_total)
#> # A tibble: 7 x 3
#>   date       title    days_total
#>   <chr>      <chr>         <int>
#> 1 2025-12-01 Carry-On         15
#> 2 2025-12-02 Carry-On         16
#> 3 2025-12-03 Carry-On         17
#> # i 4 more rows

# Titles that appeared multiple days
top10 |>
  count(title, sort = TRUE) |>
  filter(n > 3)
#> # A tibble: 8 x 2
#>   title                    n
#>   <chr>                <int>
#> 1 Carry-On                 7
#> 2 Our Little Secret        7
#> 3 The Six Triple Eight     7
#> # i 5 more rows
```

## Viewing Hours Data

Netflix publishes weekly viewing hours. This requires a Monday-Sunday date range:

```{r}
#| label: get-hours-viewed
#| eval: false
hours <- get_hours_viewed(
  platform_name   = "netflix",
  language_name   = "english",
  media_type      = "movie",
  start_date      = "2025-12-16",
  end_date        = "2025-12-22"
)

hours |>
  select(title, hours_viewed = data_value) |>
  arrange(desc(hours_viewed)) |>
  head(10)
#> # A tibble: 10 x 2
#>    title                hours_viewed
#>    <chr>                       <dbl>
#>  1 Carry-On                68500000
#>  2 The Six Triple Eight    42300000
#>  3 Our Little Secret       38100000
#> # i 7 more rows
```

## Premieres

Get upcoming releases for a platform:

```{r}
#| label: get-premieres
#| eval: false
premieres <- get_premieres(
  platform_name = "netflix",
  start_date    = "2025-12-01",
  end_date      = "2025-12-31"
)

premieres |>
  select(title = movie_data_title, premiere_date = data_premiere, type = data_type) |>
  arrange(premiere_date)
#> # A tibble: 24 x 3
#>    title                  premiere_date type
#>    <chr>                  <chr>         <chr>
#>  1 Holiday Action Film    2025-12-01    movie
#>  2 Winter Romance         2025-12-05    movie
#>  3 New Crime Series       2025-12-08    tv_show
#> # i 21 more rows
```

## Analytics Functions

### Compare Across Platforms

See how a title performs on different streaming services:

```{r}
#| label: compare-platforms
#| eval: false
compare_platforms(
  title     = "Stranger Things",
  date      = "2025-12-01",
  platforms = c("netflix", "disney+", "hbo max", "amazon prime"),
  media_type = "tv_show"
)
#> # A tibble: 4 x 4
#>   platform      rank title           date
#>   <chr>        <int> <chr>           <chr>
#> 1 netflix          1 Stranger Things 2025-12-01
#> 2 disney+         NA Stranger Things 2025-12-01
#> 3 hbo max         NA Stranger Things 2025-12-01
#> 4 amazon prime    NA Stranger Things 2025-12-01
```

### Track a Title Over Time

```{r}
#| label: title-history
#| eval: false
history <- get_title_history(
  title         = "Stranger Things",
  platform_name = "netflix",
  country_name  = "United States",
  start_date    = "2025-12-01",
  end_date      = "2025-12-07",
  media_type    = "tv_show"
)

history
#> # A tibble: 7 x 4
#>   date       title           rank platform
#>   <chr>      <chr>          <int> <chr>
#> 1 2025-12-01 Stranger Things    1 netflix
#> 2 2025-12-02 Stranger Things    1 netflix
#> 3 2025-12-03 Stranger Things    2 netflix
#> # i 4 more rows
```

### Weekly Movers

Identify which titles gained or lost positions:

```{r}
#| label: weekly-movers
#| eval: false
movers <- get_weekly_movers(
  platform_name = "netflix",
  country_name  = "United States",
  date_before   = "2025-12-14",
  date_after    = "2025-12-15",
  media_type    = "movie"
)

movers |>
  filter(status %in% c("gainer", "new_entry")) |>
  arrange(desc(change))
#> # A tibble: 5 x 5
#>   title              rank_before rank_after change status
#>   <chr>                    <int>      <int>  <int> <chr>
#> 1 New Holiday Movie           NA          2     NA new_entry
#> 2 Rising Star                  8          3      5 gainer
#> 3 Comeback Film               10          7      3 gainer
```

### Top Titles Summary

Summarize which titles dominated over a period:

```{r}
#| label: top-titles-summary
#| eval: false
summary_tbl <- get_top_titles_summary(
  platform_name = "netflix",
  country_name  = "United States",
  start_date    = "2025-12-01",
  end_date      = "2025-12-31",
  media_type    = "movie",
  n             = 10
)

summary_tbl
#> # A tibble: 10 x 6
#>    title                days_on_chart best_rank avg_rank first_seen last_seen
#>    <chr>                        <int>     <int>    <dbl> <chr>      <chr>
#>  1 Carry-On                        31         1      1.5 2025-12-01 2025-12-31
#>  2 Our Little Secret               28         1      2.3 2025-12-01 2025-12-28
#>  3 The Six Triple Eight            25         1      3.1 2025-12-01 2025-12-25
```

### Global Ranking

See how a title ranks in different countries:

```{r}
#| label: global-ranking
#| eval: false
global <- get_global_ranking(
  title         = "Stranger Things",
  platform_name = "netflix",
  date          = "2025-12-01",
  media_type    = "tv_show"
)

global |>
  filter(!is.na(rank)) |>
  arrange(rank)
#> # A tibble: 12 x 4
#>    country        rank title           date
#>    <chr>         <int> <chr>           <chr>
#>  1 United States     1 Stranger Things 2025-12-01
#>  2 Canada            2 Stranger Things 2025-12-01
#>  3 United Kingdom    3 Stranger Things 2025-12-01
#>  4 Germany           4 Stranger Things 2025-12-01
```

### Franchise Performance

Aggregate all titles in a franchise:

```{r}
#| label: franchise-performance
#| eval: false
marvel <- get_franchise_performance(
  franchise_title = "Marvel",
  platform_name   = "netflix",
  country_name    = "United States",
  start_date      = "2025-12-01",
  end_date        = "2025-12-31",
  media_type      = "movie"
)

marvel
#> # A tibble: 4 x 7
#>   title              days_on_chart best_rank avg_rank first_seen last_seen franchise
#>   <chr>                      <int>     <int>    <dbl> <chr>      <chr>     <chr>
#> 1 Black Panther                 12         3      5.2 2025-12-05 2025-12-16 Marvel
#> 2 Spider-Man: NWH                8         5      7.1 2025-12-10 2025-12-17 Marvel
```

## Lookup Tables

The package includes pre-built reference tables to avoid API calls:

```{r}
#| label: lookup-tables
#| eval: false
# View available content types
flixpatrol::flix_type_tbl
#> # A tibble: 13 x 2
#>    type_id type_label
#>      <int> <chr>
#>  1       1 movies
#>  2       2 tv
#>  3       3 anime
#>  4       4 kids
#>  ...

# View date granularities
flixpatrol::date_type_name
#> # A tibble: 7 x 2
#>   date_type_id date_type_name
#>          <int> <chr>
#>  1            1 day
#>  2            2 week
#>  3            3 month
#>  ...

# View torrent sites
flixpatrol::torrent_sites
#> # A tibble: 5 x 2
#>   torrent_site_id torrent_site_name
#>   <chr>           <chr>
#> 1 trs_1337x       1337x
#> 2 trs_eztv        eztv
#> 3 trs_piratebay   PirateBay
#> # i 2 more rows
```

## Next Steps

- Explore the [Function Reference](../../_qrtdown/reference.qmd) for complete documentation
- Check the [FlixPatrol API docs](https://flixpatrol.com/api2/) for endpoint details
- Report issues at [Codeberg](https://codeberg.org/usrbinr/flixpatrol/issues)
